\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Xuanhao Chang}} & Email : \href{mailto:chang@phys.chem.msu.ru}{chang@phys.chem.msu.ru}\\
  \href{https://www.researchgate.net/profile/Xuanhao-Chang}{ResearchGate: https://www.researchgate.net/profile/Xuanhao-Chang} & Mobile (Russia) : +7 980-011-5103 \\
  \href{https://github.com/Xuanhao-chang}{Github: https://github.com/Xuanhao-chang}                                           & Mobile (China)  : +86 15510737298 \\
  \href{https://istina.msu.ru/profile/chang/}{Istina: https://istina.msu.ru/profile/chang/}                                   &      \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lomonosov Moscow State University}{Moscow, Russia}
      {Ph.D. in Physical Chemistry; Department of Chemistry}{Sep 2019 - Sep 2023}
      
	   {\scriptsize \textit{Vibrational-rotational Molecular spectroscopy, Computational spectroscopy.}}
	    
    \resumeSubheading
      {National Research Tomsk Polytechnic University}{Tomsk, Russia}
      {Master of Physics; Research School of High-Energy Physics}{Sep 2017 - Jul 2019}
      
	   {\scriptsize \textit{High-resolution vibrational-rotational spectroscopy.}}

    \resumeSubheading
      {National Research Tomsk State University}{Tomsk, Russia}
      {Academic Mobility; Faculty of Physics}{Sep 2016 - Jul 2018}
      
	   {\scriptsize \textit{Theoritical Physics.}}

    \resumeSubheading
      {National Research Tomsk Polytechnic University}{Tomsk, Russia}
      {Bachelor of Physics; Research School of High-Energy Physics}{Aug 2015 - Jul 2017}

      \resumeSubheading
      {Jilin University}{Changchun, China}
      {Bachelor of Physics; College of Physcics}{Aug 2013 - Aug 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Chinese(Native), Russian(Advanced), English(Good skills)}
    \resumeSubItem{Programming}{Wolfram Mathematica, Fortran77/95/08 (OpenMP and Coarray), Latex, Python}
    \resumeSubItem{Tools}{Visual Studio Community/Code, Gaussian, Cfour, Origin, Windows/Lunix}
    \resumeSubItem{Knowledge and Interests}{Quantum Chemistry, Molecular ro-vibrational spectroscopy, Perturbation theory, Lie group/algebra, Differential geometry, Irreducible tensorial operator}    
\resumeSubHeadingListEnd

%-----------Awards-----------------
\section{Awards and Fellowships}
\begin{description}[font=$\bullet$]
\item {Chinese Scholarship Council Fellowship, 2015-2023} 
\end{description}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {The laboratory of quantum chemistry and molecular modeling}{Moscow, Russia}
        {Software Developer}{Sep 2019 - July 2023}
    \resumeItemListStart
    \resumeItem{ANCO program developing}{Theory and software design, debugging by comparison with Wolfram Mathematica}
    \resumeItem{RSPT, RSPT\_L, PADE programs developing}{Development in theory, debugging and analyzing}
    \resumeItemListEnd
    
    \resumeSubheading
		{Department of Chemistry, Lomonosov Moscow State University}{Moscow, Russia}
		{Teaching Assistant - Prof. Uspenskaya I.A. }{Jan 2021 - Dec 2021}
		\resumeItemListStart
        \resumeItem{Physcical Chemistry, Part I,II}{Leading weekly seminar and colloquiums}
		\resumeItemListEnd

    \resumeSubheading
		{Department of Chemistry, Lomonosov Moscow State University}{Moscow, Russia}
		{Teaching Assistant - Prof. Novakovskaya Yu.V. }{Sep 2020 - Dec 2020}
		\resumeItemListStart
        \resumeItem{Quantum Chemistry and Molecular structure}{Leading weekly seminar}
		\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Publication-----------------
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{(2023) \underline{Xuanhao C.}, Dobrolyubov E. O., Krasnoshchekov S. V.,}
{Normal Ordering of the Angular Momentum Cylindrical Ladder Operators and their Products with Wigner $D_{0,\varepsilon}^1$ functions. \\ \textbf{(To be submitted)}}

\resumeSubItem{(2023) \underline{Xuanhao C.}, Krasnoshchekov S. V.,}
{Ab initio line lists and Watson A reduction effective Hamiltonians predicted by the Van Vleck canonical operator perturbation theory.\\ \textbf{(Under Review)} }

\resumeSubItem{(2023) \underline{Xuanhao C.}, Dobrolyubov E. O., Krasnoshchekov S. V., Spectrochim. Acta A, 122071}
{Vibrational resonance analysis of linear molecules using resummation of divergent rayleigh–schrödinger perturbation theory series. \\
\href{https://doi.org/10.1016/j.saa.2022.122071}{DOI: 10.1016/j.saa.2022.122071}}

\resumeSubItem{(2022) \underline{Xuanhao C.}, Dobrolyubov E. O., Krasnoshchekov S. V., Phys. Chem. Chem. Phys., 24(11), p.6655-6675}
{Fundamental studies of vibrational resonance phenomena by multivalued resummation of divergent Rayleigh-Schrödinger perturbation theory series: deciphering polyad structures of three $H_{2} \ ^{16}O$ isotopologues. \\
\href{https://doi.org/10.1039/D1CP04279C}{DOI: 10.1039/d1cp04279c}}

\resumeSubItem{(2021) Krasnoshchekov S. V., Egor O. D., \underline{Xuanhao C.}, JQSRT, 268, 107620}
{Hypoflorous acid (hof): A molecule with a rare (1,-2,-1) vibrational resonance and (8,3,2) polyad structure revealed by padé-hermite resummation of divergent rayleigh-schrödinger perturbation theory series. \\
\href{https://doi.org/10.1016/j.jqsrt.2021.107620}{DOI: 10.1016/j.jqsrt.2021.107620}}

\resumeSubItem{(2020) Krasnoshchekov S. V., Egor O. D.,\underline{Xuanhao C.}, Optics and Spectroscopy, 128(12), p.1927-1938}
{Fundamental Analysis of Singular and Resonance Phenomena in Vibrational Polyads of the Difluorosilylene Molecule. \\
\href{https://doi.org/10.1134/S0030400X20120942}{DOI: 10.1134/S0030400X20120942}}

\resumeSubItem{(2020) \underline{Xuanhao C.}, Krasnoshchekov S. V., Pupyshev V. I., Millionshchikov D. V., Phys. Lett. A, 384(19), 126493}
{Normal ordering of the su(1, 1) ladder operators for the quasi-number states of the Morse oscillator. \\
\href{https://doi.org/10.1016/j.physleta.2020.126493}{DOI: 10.1016/j.physleta.2020.126493}}

\resumeSubItem{(2019) Krasnoshchekov S. V., \underline{Xuanhao C.}, Int. Rev. Phys. Chem., 38(1), p.63-113}
{Ladder operators for Morse oscillator and a perturbed vibrational problem. \\
\href{https://doi.org/10.1080/0144235X.2019.1593583}{DOI: 10.1080/0144235X.2019.1593583}}

\resumeSubItem{(2018) \underline{S. Chan}, O. V. Gromova, E. S. Bekhtereva, C. Leroy, O. N. Ulenikov , Russian Physics Journal, 61, p.516–520}
{Determination of Irreducible Rotational operators on the rotation SO(3) group and $T_d$ point symmetry. \\
\href{https://doi.org/10.1007/s11182-018-1428-0}{DOI: 10.1007/s11182-018-1428-0}}

\resumeSubHeadingListEnd

%-----------Presentations-----------------
\section{Presentations in International Conferences}
\resumeSubHeadingListStart
\resumeSubItem{(2023) \underline{Xuanhao C.}, Krasnoshchekov S. V.,}
{"Ab Initio Solution of the Vibration-Rotation Problem with Watson Hamiltonian by Van Vleck Operator Perturbation Theory", 
The 26th International Conference on High Resolution Molecular Spectroscopy (PRAHA2022, Aug 29th - Sep 2nd, 2022), \textbf{oral presentation}}

\resumeSubItem{(2023) \underline{Xuanhao C.}, Dobrolyubov E. O., Krasnoshchekov S. V.,}
{"Vibrational resonance analysis of acetylene using the large order perturbation series and Pade-Hermite approximant", 
The 26th International Conference on High Resolution Molecular Spectroscopy (PRAHA2022, Aug 29th - Sep 2nd, 2022), \textbf{Poster}}

\resumeSubItem{(2023) Dobrolyubov E. O., \underline{Xuanhao C.}, Krasnoshchekov S. V.,}
{"Resonance and Polyads of Carbonyl Sulphide (OCS) Isotopologues Studied by Padé-Hermite Resummation of Divergent RSPT Series", 
The 26th International Conference on High Resolution Molecular Spectroscopy (PRAHA2022, Aug 29th - Sep 2nd, 2022), \textbf{Poster}}

\resumeSubItem{(2019) \underline{Chang X.}, Krasnoshchekov S. V., Bekhtereva E.S.}
{"Ladder Operators for the Morse Oscillator and their application for a perturbed vibrational problem", 
The 26th Colloquium on High Resolution Molecular Spectroscopy (HRMS Dijon 2019, Aug 26-30, 2019), \textbf{Poster}}

\resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
